Neuroanatomical priors improve image-based cortical thickness computation: ROI-DiReCT

### 2015-10-19 manuscript.tex
Introduction
工作记忆

\begin{abstract} 
Cortical thickness measures derived from structural MRI demonstrate
reproducible associations with IQ, aging and disease and may be a
valuable biomarker for intervention studies.  Thickness of the
cortical mantle also varies predictably with neuroanatomical regions
as shown by von Economo in 1927.  Recent research demonstrates that
training segmentation data is able to automatically partition the
cortex into major neuroanatomical divisions.  The correlation of
neuroanatomical region and cortical thickness implies that cortical
labeling may improve cortical thickness quantification by introducing
additional prior information.  We thus propose a new solution,
ROI-DiReCT, to image-based cortical thickness estimation (ICTE)
that leverages recent advances in multi-template labeling, distributed
computing and reproducible research to both extend and validate prior
work.  We use an open-source image processing toolkit and public data
to test the hypothesis that additional priors introduced through
cortical parcellation can be used in a divide-and-conquer strategy to
improve the accuracy and speed of ICTE.  For instance, the expected
range of cortical thickness in post-central gyrus differs from that of
inferior temporal gyrus and, via ROI-DiReCT, this information may
be included in the thickness estimation.  We use the semi-manually labeled NIREP
data to contrast whole-brain ICTE with those gained by ROI-DiReCT
with respect to known patterns of cortical thickness values as
provided by von Economo and others.  We also use multi-template
labeling, based on NIREP, to automatically label the T1 images from
the multi-modality reproducibility dataset.  This allows us to compare
the reproducibility of our whole-brain and ROI-DiReCT ICTE.
ROI-DiReCT provides more stable and neuroanatomically plausible
results.
\end{abstract}

@@

in pumed, look at cortical thickness parcellation

>>>>

\begin{abstract} 
abstract
\end{abstract}

@@

Working memory is a temporal process to maintain and manipulate information over short periods of time. WM has been shown to be impaired in many neurological and psychiatric syndromes including Schizophrenia. It was thought to be tightly associated with cognitive deficits in Schizophrenia. WM itself is a complex process which has been multidimensionally related to the psychosis.
Thus, a examination of the underlying neurological mechanism provided us with insight into the causes, progression and even treatment of schizophrenia. There has been abundant imaging studies in this area, but the differences among the tasks and material make it difficult to make a conclusion. There have been evidence of multi-modality deficits: visual spatial, visual object, verbal, and other types of working memory. One popular and original model of WM is a system encoding and maintaining modality-specific short-term memory and central executive component to manipulate the information.
